Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-30 bbbq_article.tex

Presentation of antigens by MHC-II is important for the activation of
B cells, because B cells present peptides in MHC-II to helper T cells.  
Interestingly, the CB cell produce antibodies that recognize only solvent-exposed protein regions,
thus the B cell receptor is inherently unable to present hydrophobic regions.
Our analysis suggests, however, that MHC-II
over-presents TMH regions. A helper T cell thus needs an 
\geert{
  Beter is zeggen dat (1) MHC-II presentatie belangrijk is voor B cell activatie. (2) B cellen antilichamen produceren, en dan antilichamen solvent-exposed protein regions herkennen. (3) Dat onze analyse suggereert HMC-II presentatie voornamelijk andere (TMH of buried) regio's betreft. (4) Dat T helper cellen dus andere delen van antigene eiwitten herkennen (MHC-II gepresenteerd door de B cellen) dan de BCR bindt.
}

>>>>

Our study also suggests that T cells will largely recognize different protein regions than B cells. Presentation of antigens by MHC-II is important for the activation of
naive B cells by helper T cells. For this activation, B cells first ingest antigen that is bound to their B cell receptor, and subsequently present peptides derived from this antigen in MHC-II to helper T cells. Following their activation by the T cells, B cells mature into plasma cells and release antibodies which recognize the same part of the antigen as the original B cell receptor. B cell receptors and antibodies will thus recognize solvent-exposed regions of antigens that are accessible for binding to the B cell receptor. However, the results from our study predict that most MHC-II haplotypes present relatively hydrophobic peptides, which are less likely to be solvent exposed. It is unknown why B and T cells seem to predominantly recognize different protein regions, but one possibility might be that this lowers the chance of B cell mediated autoimmune diseases, because auto-reactive B and T cells recognizing different part of the same antigen would need to be present for breakage of B cell tolerance.
